A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-11 manuscript/manuscript.tex
added all figures to latex document

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\author{
	Thomas G. Close \and
	Phillip G. D. Ward  \and
	Francesco Sforazzini  \and
	Wojtek Goscinski  \and
	Zhaolin Chen  \and
	Gary F. Egan  \and
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              \email{tom.close@monash.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

%\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}

\textbf{Figure 1} - Example study. Blue boxes represent acquired (input)
data (filesets or fields) stored in a repository and green derivatives
from that data stored alongside the original data. Orange ovals are
pipelines that operate on data in the repository to derive the
derivatives. Arrows represent data flows, i.e., inputs and outputs to
pipelines.

@@

%\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}

\textbf{Figure 2} - Simplified Unified Modelling Language (UML) diagram
of information flow in the Arcana framework. Boxes: Python classes,
blue=analysis-design, green=analysis-application. Arrows: orange=data,
magenta=workflow description, diamond=aggregated-in. Study classes
construct analysis pipelines, which are sent to the \emph{Processor} to
be processed. Input data is selected by \emph{Selector} objects and
pulled to the compute environment to be processed along with existing
intermediate derivatives. After the derivatives are pushed back to the
repository.

@@

%\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}

\textbf{Figure 6} - Example MultiStudy. Blue boxes represent acquired
(input) data (filesets or fields) and green derivatives. Orange ovals
are pipelines. Blue and green arrows: acquired and derived inputs to
pipelines, respectively. Orange arrows: outputs of pipelines. Dashed
boxes represent data specifications in a sub-study that are present in
the global namespace and mapped into the sub-study space, and dotted
arrows the mappings. Sub-studies are linked by mapping the same data
spec in the global space onto data specifications the multiple sub-study
namespaces (e.g. \emph{Derived 1, 2 \& 3}). There are no restrictions
between mapping acquired and derivative specifications: both acquired
and derivative specifications can be mapped onto acquired data or
derivative specifications in sub-studies. If a spec in the global spaced
is mapped onto a derivative spec in the sub-study space, then the
pipeline that generates that derivative in the sub-study will not run
unless it generates other required derivatives (e.g. \emph{Pipeline 3}).

@@

%\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}

\textbf{Figure 7} - Detailed Unified Modelling Language (UML) diagram of
information flow in the Arcana framework. Boxes: Python classes
(blue=core, green=interchangeable modules, grey=example
specialisations). Arrows: orange=data, magenta=workflow description,
diamond=aggregated-in, triangle=subclass-of. Calling \emph{data(name)}
on a Study subclass constructs the requisite pipelines (as specified in
\emph{Study.data\_specs}) to produce the requested data, and sends them
to the \emph{Processor} to be processed. Data is selected by
\emph{Selector} objects, pulled to the compute environment to be
processed, and then the derivatives are pushed back to the repository.
Repositories can be of plain directories, or BIDS or XNAT repositories.

@@

%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure 8} - Example application of Study class to a dataset stored in an XNAT
%repository. Once the Study object has been initialised potential
%derivatives of the Study can be requested, and will be generated and
%stored in the repository if already present.

@@

Summary data (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
\emph{per\_study} frequencies\emph{)} are stored in specially named
subjects and visits (e.g. `all'), the names for which are specified when
the repository is initialised. For example, given in plain-directory
repository using all as the summary name for both subjects and visits,
per\_subject data for `subj1' would be stored at
\emph{\textless{}root-dir\textgreater{}/subj1/}all, per\_visit data for
`visit1' in \emph{\textless{}root-dir\textgreater{}/}all\emph{/visit1},
and per\_study data in \emph{\textless{}root\_dir\textgreater{}/}all/all
(Table 1).

\begin{longtable}[]{@{}llll@{}}
\toprule
& \textbf{Plain-directory} & \textbf{BIDS} &
\textbf{XNAT}\tabularnewline
\midrule
\endhead
\textbf{Derivatives} & \emph{/subject/visit/study} &
/derivatives/study/subject/visit &
/subject/\emph{visit\_study}\tabularnewline
\textbf{Fields} & \emph{.../}\_\_fields\_\_\emph{.json} &
\emph{.../}\_\_fields\_\_\emph{.}json & ``custom
variables''\tabularnewline
\textbf{Provenance} & \emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
\emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
.../scans/\_\_prov\_\_/resources/\emph{pipeline/}prov\emph{.}json\tabularnewline
\textbf{per\_subject} & \emph{/subject/}all\emph{/study} &
\emph{/derivatives/study/subject/}all &
\emph{/subject/}all\_\emph{study}\tabularnewline
\textbf{per\_visit} & \emph{/}all\emph{/visit/study} &
\emph{/derivatives/study/}all\emph{/visit} &
\emph{/}all\emph{/visit\_study}\tabularnewline
\textbf{per\_study} & \emph{/}all\emph{/}all\emph{/study} &
\emph{/derivatives/study/}all\emph{/}all &
\emph{/}all\emph{/}all\_\emph{study}\tabularnewline
\bottomrule
\end{longtable}

\textbf{Table 1} - Storage locations of derived data for each repository
type. Derivatives are stored in separate namespaces for each Study
instance to enable multiple analyses on the same datasets with different
parameterisations. `...' refers to the \emph{Derivatives}
directory/xnat:MrSession.

@@

\textbf{Figure 9} - Example diffusion MRI (dMRI) study, which can derive
tensor metrics, fractional anisotropy (FA) and apparent diffusion
coefficient (ADC) as well as streamlines fibre tracking. Blue boxes:
acquired (input) data (filesets or fields). Green boxes: derivatives.
Orange ovals: pipelines. Blue and green arrows: acquired and derived
inputs to pipelines, respectively. Orange arrows: outputs of pipelines.
The dMRI magnitude image is preprocessed for motion correction and EPI
distortions masked and bias corrected. From the bias corrected image two
branches of analysis can be performed using the same intermediate
derivatives: FA and ADC and/or streamlines fibre tracking.

@@

\textbf{Figure 10} - Combined T1-weighted/T2*-weighted multi-study,
which can derive vein masks by combining Quantitative Susceptibility
Mapping (QSM) and Susceptible Weighted Imaging (SWI) contrasts with a
manual atlas. Blue boxes: acquired (input) data (filesets or fields).
Green boxes: derivatives. Orange ovals: pipelines. Blue and green
arrows: acquired and derived inputs to pipelines, respectively. Orange
arrows: outputs of pipelines. Dashed boxes represent data specifications
in a sub-study that are present in the global namespace and mapped into
the sub-study space, and dotted arrows the mappings. The acquired
T1-weighted image is mapped to both the \emph{magnitude} spec of the
T1-weighted sub-study and the \emph{registration reference} spec of the
T2*-weighted sub-study. The nonlinear transformation from subject to
atlas space are mapped from the T1-weighted sub-study and combined with
the linear registration between T1-weighted and T2*-weighted images, QSM
and SWI images mapped from the T2*-weighted sub-study to produce the
composite-vein image. The brain mask from the T1-weighted sub-study is
combined with the composite vein image to produce the vein mask.

@@

Figure 11 displays composite vein images and vein masks for the healthy
volunteer along with the SWI and QSM intermediate derivatives and the
input vein atlas. The derived vein images are comparable to those
generated by the original implementation (Ward 2018). The complete
workflow took ?? min to complete over ?? compute cores.

@@

\textbf{Figure 11 -} Vein image (\emph{right column}) constructed by
combining susceptibility weighted imaging (SWI) (\emph{left column}),
quantitative susceptibility mapping (QSM) (\emph{left-middle column})
and a vein atlas from manual tracings (\emph{right-middle column}).
\emph{Top row}: sagittal slices. \emph{Middle row}: axial slices.
\emph{Bottom row}: coronal slices.

Figure 12 displays the FA and ADC maps derived from the diffusion MRI
acquisition. The FA map shows high intensity in known white matter
tracts and low intensities in known grey matter regions. The ADC map
shows high intensity in cortical spinal fluid and low intensity through
the rest of the brain.

@@

\textbf{Figure 12 -} Fractional Anisotropy (FA) \emph{(top row)} and
Apparent Diffusion Coefficient (ADC) (\emph{bottom rowI)} derived from
diffusion MRI data. \emph{Left column:} axial midline slices.
\emph{Middle column:} coronal midline slices. \emph{Left column}:
sagittal midline slices.

Figure 12 displays the global tractography derived from the dMRI
acquisition. The streamlines follow well known white matter tracts such
as the cortico-spinal, fasciculus and corpus callosum. Intermediate
derivatives derived for the FA and ADC analysis, including the
preprocessed and bias-corrected dMRI image and a whole brain mask, were
reused in the generation of the streamlines reducing the time taken to
produce the tractography results from ?? to ??.

@@

\textbf{Figure 13 -} Global tractography performed using the MRtrix
toolbox. Probabilistic streamlines generated with the iFOD2 algorithm
from fibre Orientation Distribution Function (fODF) estimated from
diffusion MRI datasets using Constrained Spherical Deconvolution (CSD).
Streamlines are colour-encoded by orientation: green=anterior-posterior,
blue=inferior-superior, red=left-right. \emph{Left panel:} axial midline
slice. \emph{Middle panel:} coronal midline slice. \emph{Left panel}:
sagittal midline slice.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}

% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}

\newcommand{\D}{...}
\newcommand*{\affaddr}[1]{#1}
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}

%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\author{
	Thomas G. Close\affmark[1,2]\and
	Phillip G. D. Ward\affmark[1,3,4] \and
	Francesco Sforazzini\affmark[1] \and
	Wojtek Goscinski\affmark[6] \and
	Zhaolin Chen\affmark[1,5] \and
	Gary F. Egan\affmark[1,3,4]
}

\authorrunning{
        Thomas G. Close \and
	Phillip G. D. Ward  \and
	Francesco Sforazzini  \and
	Wojtek Goscinski  \and
	Zhaolin Chen  \and
	Gary F. Egan  \and} % if too long for running head

\institute{
	Thomas G. Close \at
	 \email{tom.close@monash.edu} \\ \\
         \affaddr{\affmark[1]Monash Biomedical Imaging, Monash University, Melbourne, Australia} \\
         \affaddr{\affmark[2]Australian National Imaging Facility, Australia} \\
         \affaddr{\affmark[3]Australian Research Council Centre of Excellence for integrative Brain Function, Melbourne, Australia} \\
         \affaddr{\affmark[4]Monash Institute of Cognitive and Clinical Neurosciences, Monash University, Melbourne, Australia} \\
         \affaddr{\affmark[5]Department of Electrical and Computer Systems Engineering, Monash University, Melbourne, Australia} \\
         \affaddr{\affmark[6]Monash eResearch Centre, Monash University, Melbourne, Australia} \\
}

%\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.55\textwidth]{figures/example_study}
  \caption{Example study. Blue boxes represent acquired (input)
data (filesets or fields) stored in a repository and green derivatives
from that data stored alongside the original data. Orange ovals are
pipelines that operate on data in the repository to derive the
derivatives. Arrows represent data flows, i.e., inputs and outputs to
pipelines}
  \end{center}
\label{fig:example_study}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.9\textwidth]{figures/simplified_arcana_uml}
  \caption{Unified Modelling Language (UML) diagram
of information flow in the Arcana framework. Boxes: Python classes,
blue=analysis-design, green=analysis-application. Arrows: orange=data,
magenta=workflow description, diamond=aggregated-in. Study classes
construct analysis pipelines, which are sent to the \emph{Processor} to
be processed. Input data is selected by \emph{Selector} objects and
pulled to the compute environment to be processed along with existing
intermediate derivatives. After the derivatives are pushed back to the
repository.}
\end{center}
\label{fig:simple_uml}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.775\textwidth]{figures/example_multi_study}
  \caption{Example MultiStudy. Blue boxes represent acquired
(input) data (filesets or fields) and green derivatives. Orange ovals
are pipelines. Blue and green arrows: acquired and derived inputs to
pipelines, respectively. Orange arrows: outputs of pipelines. Dashed
boxes represent data specifications in a sub-study that are present in
the global namespace and mapped into the sub-study space, and dotted
arrows the mappings. Sub-studies are linked by mapping the same data
spec in the global space onto data specifications the multiple sub-study
namespaces (e.g. \emph{Derived 1, 2 \& 3}). There are no restrictions
between mapping acquired and derivative specifications: both acquired
and derivative specifications can be mapped onto acquired data or
derivative specifications in sub-studies. If a spec in the global spaced
is mapped onto a derivative spec in the sub-study space, then the
pipeline that generates that derivative in the sub-study will not run
unless it generates other required derivatives (e.g. \emph{Pipeline 3} in
\emph{Sub-Study2})}
\end{center}
\label{fig:example_multi_study}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/full_arcana_uml}
  \caption{Detailed Unified Modelling Language (UML) diagram of
information flow in the Arcana framework. Boxes: Python classes
(blue=core, green=interchangeable modules, grey=example
specialisations). Arrows: orange=data, magenta=workflow description,
diamond=aggregated-in, triangle=subclass-of. Calling \emph{data(name)}
on a Study subclass constructs the requisite pipelines (as specified in
\emph{Study.data\_specs}) to produce the requested data, and sends them
to the \emph{Processor} to be processed. Data is selected by
\emph{Selector} objects, pulled to the compute environment to be
processed, and then the derivatives are pushed back to the repository.
Repositories can be of plain directories, or BIDS or XNAT repositories}
\label{fig:full_uml}
\end{center}
\end{figure*}

@@

%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}

Listing - Example application of Study class to a dataset stored in an XNAT
repository. Once the Study object has been initialised potential
derivatives of the Study can be requested, and will be generated and
stored in the repository if already present.

@@

Summary data (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
\emph{per\_study} frequencies\emph{)} are stored in specially named
subjects and visits (e.g. `all'), the names for which are specified when
the repository is initialised. For example, given in plain-directory
repository using all as the summary name for both subjects and visits,
per\_subject data for `subj1' would be stored at
\emph{\textless{}root-dir\textgreater{}/subj1/}all, per\_visit data for
`visit1' in \emph{\textless{}root-dir\textgreater{}/}all\emph{/visit1},
and per\_study data in \emph{\textless{}root\_dir\textgreater{}/}all/all
(Table \ref{tbl:repo-structure}).

\begin{table}
% table caption is above the table
\caption{Storage locations of derivative and provenance data for each repository
type. Derivatives are stored in separate namespaces for each Study
instance to enable multiple analyses on the same datasets with different
parameterisations. Where `...' = \emph{derivatives}
directory/XNAT session, \emph{subj} = subject ID, \emph{vis} = visit ID,
\emph{study} = name of the Study instance, and \emph{pl} = name
of pipeline.}
\label{tbl:repo-structure}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{llll}
\hline\noalign{\smallskip}
\textbf{Type} & Plain-directory & BIDS & XNAT  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Deriv.} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study} \\
\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & ``custom vars.'' \\
\textbf{Prov.} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}/prov\emph{.}json \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.55\textwidth]{figures/dmri_study}
  \caption{Example diffusion MRI (dMRI) study, which can derive
tensor metrics, fractional anisotropy (FA) and apparent diffusion
coefficient (ADC) as well as streamlines fibre tracking. Blue boxes:
acquired (input) data (filesets or fields). Green boxes: derivatives.
Orange ovals: pipelines. Blue and green arrows: acquired and derived
inputs to pipelines, respectively. Orange arrows: outputs of pipelines.
The dMRI magnitude image is preprocessed for motion correction and EPI
distortions masked and bias corrected. From the bias corrected image two
branches of analysis can be performed using the same intermediate
derivatives: FA and ADC and/or streamlines fibre tracking.}
\end{center}
\label{fig:dmri_study}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.775\textwidth]{figures/t2star_t1_study}
  \caption{Combined T2*-weighted/T1-weighted multi-study,
which can derive vein masks by combining Quantitative Susceptibility
Mapping (QSM) and Susceptible Weighted Imaging (SWI) contrasts with a
manual atlas. Blue boxes: acquired (input) data (filesets or fields).
Green boxes: derivatives. Orange ovals: pipelines. Blue and green
arrows: acquired and derived inputs to pipelines, respectively. Orange
arrows: outputs of pipelines. Dashed boxes represent data specifications
in a sub-study that are present in the global namespace and mapped into
the sub-study space, and dotted arrows the mappings. The acquired
T1-weighted image is mapped to both the \emph{magnitude} spec of the
T1-weighted sub-study and the \emph{registration reference} spec of the
T2*-weighted sub-study. The nonlinear transformation from subject to
atlas space are mapped from the T1-weighted sub-study and combined with
the linear registration between T1-weighted and T2*-weighted images, QSM
and SWI images mapped from the T2*-weighted sub-study to produce the
composite-vein image. The brain mask from the T1-weighted sub-study is
combined with the composite vein image to produce the vein mask.}
  \end{center}
\label{fig:t2star_t1_study}
\end{figure*}

@@

Figure \ref{fig:veins} displays composite vein images and vein masks for the healthy
volunteer along with the SWI and QSM intermediate derivatives and the
input vein atlas. The derived vein images are comparable to those
generated by the original implementation (Ward 2018). The complete
workflow took ?? min to complete over ?? compute cores.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/veins}
  \caption{Vein image (\emph{right column}) constructed by
combining susceptibility weighted imaging (SWI) (\emph{left column}),
quantitative susceptibility mapping (QSM) (\emph{left-middle column})
and a vein atlas from manual tracings (\emph{right-middle column}).
\emph{Top row}: sagittal slices. \emph{Middle row}: axial slices.
\emph{Bottom row}: coronal slices.}
  \end{center}
\label{fig:veins}
\end{figure*}

Figure \ref{fig:fa_adc}  displays the FA and ADC maps derived from the diffusion MRI
acquisition. The FA map shows high intensity in known white matter
tracts and low intensities in known grey matter regions. The ADC map
shows high intensity in cortical spinal fluid and low intensity through
the rest of the brain.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/fa_adc}
  \caption{Fractional Anisotropy (FA) \emph{(top row)} and
Apparent Diffusion Coefficient (ADC) (\emph{bottom rowI)} derived from
diffusion MRI data. \emph{Left column:} axial midline slices.
\emph{Middle column:} coronal midline slices. \emph{Left column}:
sagittal midline slices.}
  \end{center}
\label{fig:fa_adc}
\end{figure*}

Figure \ref{fig:tractography} displays the global tractography derived from the dMRI
acquisition. The streamlines follow well known white matter tracts such
as the cortico-spinal, fasciculus and corpus callosum. Intermediate
derivatives derived for the FA and ADC analysis, including the
preprocessed and bias-corrected dMRI image and a whole brain mask, were
reused in the generation of the streamlines reducing the time taken to
produce the tractography results from ?? to ??.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/tractography}
  \caption{Global tractography performed using the MRtrix
toolbox. Probabilistic streamlines generated with the iFOD2 algorithm
from fibre Orientation Distribution Function (fODF) estimated from
diffusion MRI datasets using Constrained Spherical Deconvolution (CSD).
Streamlines are colour-encoded by orientation: green=anterior-posterior,
blue=inferior-superior, red=left-right. \emph{Left panel:} axial midline
slice. \emph{Middle panel:} coronal midline slice. \emph{Left panel}:
sagittal midline slice.}
  \end{center}
\label{fig:tractography}
\end{figure*}

@@

\section*{Acknowlegements}
We would like to acknowledge the generous support of
